---
title: "HW week 12"
author: "Arisa Nguyen, Ayman Bari, Emanuel Mejía, Jorge Bonilla"
subtitle: |
  | w203 teaching team
  | w203: Statistics for Data Science

output:
  pdf_document: default
  html_document: default
---

```{r load packages, message = FALSE, warning = FALSE}
library(tidyverse)
library(ggplot2) 
library(lmtest)
library(sandwich)
library(stargazer)
library(janitor)
library(car)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r source functions from project, echo = FALSE}
source('./src/load_and_clean.R')
source('./src/get_robust_se.R')
```

```{r load data} 
d <- load_and_clean(input = 'videos.txt')

d %>% summarise(across(everything(),~sum(is.na(.))))
d <- d %>% filter(!is.na(length))
d <- d %>% filter(length < 660)
mean_rating <- mean(d$average_rating, na.rm = TRUE)
d[d$average_rating == 0, "average_rating"] <- mean_rating
```

```{r data quality checks}

# Count the number of videos where the video id is invalid.
sum(d$video_id == "#NAME?")

# Count the number of videos that do no have a length of eleven characters.
sum(nchar(as.character(d$video_id)) != 11)

# Count the number of views recorded as NA
sum(is.na(d$views))

```

# Regression analysis of YouTube dataset

You want to explain how much the quality of a video affects the number of views it receives on social media. In a world where people can now buy followers and likes, would such an investment increase the number of views that their content receives?  **This is a causal question.** 

You will use a dataset created by Cheng, Dale and Liu at Simon Fraser University.  It includes observations about 9618 videos shared on YouTube.  Please see [this link](http://netsg.cs.sfu.ca/youtubedata/) for details about how the data was collected.

You will use the following variables:

- `views`: the number of views by YouTube users.
- `average_rating`: This is the average of the ratings that the video received, it is a renamed feature from `rate` that is provided in the original dataset. (Notice that this is different from `cout_of_ratings` which is a count of the total number of ratings that a video has received. 
- `length:` the duration of the video in seconds.

a. Perform a brief exploratory data analysis on the data to discover patterns, outliers, or wrong data entries and summarize your findings.

```{r conduct EDA in this chunk, warning = FALSE, out.width='80%', fig.align='center'}

# Data Summary
summary(d)

# Views 
hist_views <- d %>% 
  ggplot() + 
  aes(x = log10(views)) + 
  geom_histogram(bins = 100, fill = "#001F82") + 
  labs(title = 'Distribution of Views', x = 'log10(Views)', y = 'Count') + 
  theme_classic() +
    theme(
      plot.title = element_text(color = "#0099F8",
                                size = 17,
                                face = "bold"),
      plot.subtitle = element_text(size = 13, face = "italic"),
      axis.title = element_text(color = "#969696",
                                size = 10,
                                face = "bold"),
      axis.text = element_text(color = "#969696", size = 10),
      axis.line = element_line(color = "#969696")
    )

hist_views

# Rating
hist_rate <- d %>% 
  ggplot() + 
  aes(x = average_rating) + 
  geom_histogram(breaks = seq(0.5,5.5), fill = "#833C0C") + 
  labs(title = 'Distribution of Ratings', x = 'Average Ratings', y = 'Count') + 
  theme_classic() +
    theme(
      plot.title = element_text(color = "#ED7D31",
                                size = 17,
                                face = "bold"),
      plot.subtitle = element_text(size = 13, face = "italic"),
      axis.title = element_text(color = "#969696",
                                size = 10,
                                face = "bold"),
      axis.text = element_text(color = "#969696", size = 10),
      axis.line = element_line(color = "#969696")
    )
hist_rate

# Length
hist_length <- d %>% 
  ggplot() + 
  aes(x = log10(length)) + 
  geom_histogram(bins = 100, fill = "#375623") + 
  labs(title = 'Distribution of Length', x = 'log10(Length)', y = 'Count') + 
  theme_classic() +
    theme(
      plot.title = element_text(color = "#70AD47",
                                size = 17,
                                face = "bold"),
      plot.subtitle = element_text(size = 13, face = "italic"),
      axis.title = element_text(color = "#969696",
                                size = 10,
                                face = "bold"),
      axis.text = element_text(color = "#969696", size = 10),
      axis.line = element_line(color = "#969696")
    )
hist_length


```

> 'From this EDA, we learn that there are 9 rows with NA value for views, rating, and length, and should be excluded from further analysis. The minimum value of views is 3 and the maximum is 1,807,640 which is in the realm of possibility. The minimum value of average_ratings is 0 and the maximum value is 5, which is also in the realm of possibility since the Youtube rating system used to range from 0 to 5 stars. The minimum and maximum value for length is 1 second and 5289 seconds (or about 1.5 hours), which also seems plausible. 
Views and length were both log transformed to normalize its distributions and to eliminate the effect of outliers. After this transformation, views had a normal distribution ranging from 0 to 10^6 views with the peak being at about 10^3 views. Length has a multimodal distribution peaking at about 10^2.4 and 10^2.8 seconds and ranged from 10^0.5 and 10^2.8 seconds. Ratings were distributed between 0 to 5 with the highest peaks occuring at 0 and 5 and smaller peaks at 1, 3, and 4. The high count of videos around whole number ratings may be indicating that many videos receive very few or no rating. Another theory is the ratings tend to cluster around one ratings which may stem from the selection bias associated with viewers having a higher probability to provide low scores to videos they disliked or high ratings to videos they enjoyed. It appears that the most viewers opt for binary ratings as represented in the bimodal distribution of the Ratings histogram. The idea is that dissatisfied viewers and highly satisfied viewers have a disproportionaly higher voting turnout than moderately or lowly satisfied viewers.'


b. Based on your EDA, select an appropriate variable transformation (if any) to apply to each of your three variables.  You will fit a model of the type,

$$
  f(\text{views}) = \beta_0 + \beta_1 g(\text{rate})  + \beta_3 h(\text{length})
$$ 

Where $f$, $g$ and $h$ are sensible transformations, which might include making *no* transformation. 

```{r fit a regression model here}
model <- lm(log10(views) ~ average_rating + log10(length), data = d) 

stargazer(
   model, 
   type = 'text', 
   se = list(get_robust_se(model))
   )
```

```{r include = FALSE}
y_lm <- log10(d$views)
x_1 <- d$average_rating
x_2 <- log10(d$length)
```


c. Using diagnostic plots, background knowledge, and statistical tests, assess all five assumptions of the CLM. When an assumption is violated, state what response you will take.  As part of this process, you should decide what transformation (if any) to apply to each variable. Iterate against your model until your satisfied that at least four of the five assumption have been reasonably addressed. 

> 1. **IID Data:** 'For the CLM to apply, we requrie that our data is generated by an IID sampling process. In this case, a web crawler was used to collect the video data about YouTube videos. The crawler used a directed graph when sampling videos (directional links between videos, where each node represents a video). The initial videos (root 0 in the graph), were pre-selected by the researchers (from currated pages on the YoueTube platform, such as "Most Viewed", or "Top Rated"). The following videos added to the sample (and to the graph, by the crawler) were selected from the list of videos related to each video already in the sample (adding 20 videos with each step, and going to a depth of 4). While the sample size is large, this method sampling method can not be considered random as we are relying on a currated (non-independent) initial sample, based on some common criteria, then adding further related videos, violiting our requirement for independance in the sample.'


> 2. **No Perfect Colinearity:** 'We are using two variables, namely average rating and length, which don't seem perfect colinear from their very definition since they don't seem to be different ways to say the same concept, one talks about the perceived quality while the other is the video's duration. When computing their correlation: $\rho =$ `r round(cor(d$average_rating,d$length, method = "pearson"), digits=3)`, we can notice that indeed they don't seem highly correlated, and therefore neither colinear.'



> 3. **Linear Conditional Expectation:** 'When looking at our scatterplot of Predicted Values and their Residuals, there seems to be a linear conditicional expectation for the residuals. So even when the graph for our first X (Average rating) might not look as linear as desired, we could say that this assumption is fairly met.'

```{r include = FALSE}
d$pred <- model$fitted.values
d$res <- model$residuals
```


```{r code and plots assessing linear conditional expectation , message = FALSE , out.width="70%", fig.align = "center"}
d %>% ggplot(aes(x = d$pred, y = d$res)) + geom_point(color = "#001F82") + 
  stat_smooth(color = "#0099F8") +   
  labs(title = "Predicted Values VS Residuals",
       subtitle = "Scatterplot",
       x = "Predicted log(Views)",
       y = "Residuals") +
  theme_minimal() +
    theme(
      plot.title = element_text(color = "#0099F8",
                                size = 17,
                                face = "bold"),
      plot.subtitle = element_text(size = 13, face = "italic"),
      axis.title = element_text(color = "#969696",
                                size = 10,
                                face = "bold"),
      axis.text = element_text(color = "#969696", size = 10),
      axis.line = element_line(color = "#969696")
    )
```

```{r fig.show="hold", out.width="50%", message = FALSE}
d %>% ggplot(aes(x = x_1, y = d$res)) + geom_point(color = "#833C0C") + 
  stat_smooth(color = "#ED7D31") +   
  labs(title = "Average Rating VS Model Residuals",
       subtitle = "Scatterplot",
       x = "Avg Rating",
       y = "Residuals") +
  theme_minimal() +
    theme(
      plot.title = element_text(color = "#ED7D31",
                                size = 17,
                                face = "bold"),
      plot.subtitle = element_text(size = 13, face = "italic"),
      axis.title = element_text(color = "#969696",
                                size = 10,
                                face = "bold"),
      axis.text = element_text(color = "#969696", size = 10),
      axis.line = element_line(color = "#969696")
    )

d %>% ggplot(aes(x = x_2, y = d$res)) + geom_point(color = "#375623") +
    stat_smooth(color = "#70AD47") +   
  labs(title = "log(Length) VS Model Residuals",
       subtitle = "Scatterplot",
       x = "log(Length)",
       y = "Residuals") +
  theme_minimal() +
    theme(
      plot.title = element_text(color = "#70AD47",
                                size = 17,
                                face = "bold"),
      plot.subtitle = element_text(size = 13, face = "italic"),
      axis.title = element_text(color = "#969696",
                                size = 10,
                                face = "bold"),
      axis.text = element_text(color = "#969696", size = 10),
      axis.line = element_line(color = "#969696")
    )
```


> 4. **Homoskedastic Errors:** 'When assessing homoskedastic errors, we are looking for evidence that heteroskedacicity exists among the errors. Since the p-value after performing the Breusch-Pagan test is < 2.2e-16 which is smaller than our alpha of 0.05, we reject the null hypothesis that there is no evidence of heteroskedasticity. The "Predicted Values VS Residuals" plot from the previous point also shows that our model suffers from heteroskedastic error because residuals seem further away from zero as the predicted value gets bigger. The assumption of homoskedastic error is not met.'

```{r code and plots assessing error variance}
bptest(model)
```

> 5. **Normally Distributed Errors:** 'When looking at the distribution of our residuals we find indeed a bell-shaped density, which is confirmed when comparing it with a normal distribution using a Q-Q Plot. This assumption is satisfied in this case'

```{r code and plots assessing normally distributed errors, fig.show="hold", out.width="50%"}
d %>% ggplot(aes(res)) +
    labs(
      title = "Model Residuals",
      subtitle = "Density Plot",
      x = "Residuals",
      y = "Density"
    ) +
    theme_classic() +
    theme(
      plot.title = element_text(color = "#0099F8",
                                size = 17,
                                face = "bold"),
      plot.subtitle = element_text(size = 13, face = "italic"),
      axis.title = element_text(color = "#969696",
                                size = 10,
                                face = "bold"),
      axis.text = element_text(color = "#969696", size = 10),
      axis.line = element_line(color = "#969696")
    ) + geom_density(color = "#00558A", fill = "#71C9FF", alpha = 0.6) 

d %>% ggplot(aes(sample = scale(res))) + 
  geom_qq(color = "#0099F8") +
  geom_abline(alpha=0.5) +
  labs(title = "Model Residuals",
       subtitle = "Normality Test (Quantile-Quantile Plot)") +
  theme_minimal() +
    theme(
      plot.title = element_text(color = "#0099F8",
                                size = 17,
                                face = "bold"),
      plot.subtitle = element_text(size = 13, face = "italic"),
      axis.title = element_text(color = "#969696",
                                size = 10,
                                face = "bold"),
      axis.text = element_text(color = "#969696", size = 10),
      axis.line = element_line(color = "#969696")
    )
```